---
title: "The Usefulness of Financial Accounting Information: Analysis for Online Experiment"
author: Stefano Cascino, Mark Clatworthy, Beatriz García Osma, Joachim Gassen and Shahed Imam
output: html_document
date: '2020-09-28'
---


``` {r setup, include = FALSE}
library(car)
library(tidyverse)
library(lubridate)
library(lfe)
library(ExPanDaR)
library(scales)


knitr::opts_chunk$set(echo = TRUE, table.align = "center", cache.lazy = FALSE, 
                      message = FALSE, error = FALSE, warning = FALSE, 
                      clean = FALSE, fig.align="center")
library(knitr)
opts_knit$set(root.dir = "..")
library(kableExtra)

```


## Sample construction

```{r data_import, cache=TRUE}
resp <- read_csv("online_experiment/data/online_exp_response_data.csv")
emails <- read_csv("online_experiment/data/online_exp_emails_sent.csv")
```

```{r sample_table, fig.width = 10}
resp  %>%
    filter(!is.na(time_read)) %>%
    mutate(tstamp = ymd_hms(tstamp)) %>%
    ggplot(aes(x = tstamp)) + 
    geom_histogram(binwidth=3600) +
    scale_x_datetime(
      name = "Date and time [UTC]",
      date_labels = "%b %d", 
      date_breaks = "1 day",
      date_minor_breaks = "6 hours",
      limits = c(ymd_hms("2019-06-26 00:00:00"), 
                 ymd_hms("2019-07-16 11:49:08")),
      expand = c(0,0)) +
    ylab("Responses per hour") +
    theme_minimal()

sent_wave <- as.data.frame(table(emails$wave), stringsAsFactors = FALSE)
colnames(sent_wave) <- c("wave", "emails_sent")
sent_wave <- cbind(sent_wave, group = c("Portfolio Manager, Rest of World",
                                        "Portfolio Manager, Europe",
                                        "Portfolio Manager, North America",
                                        "Financial Analysts, Rest of World",
                                        "Financial Analysts, Europe",
                                        "Financial Analysts, North America"))
sent_wave$occupation <- c(rep("Portfolio Manager", 3), rep("Financial Analyst", 3))
sent_wave$location <- rep(c("Rest of World", "Europe", "North America"), 2)

resp %>%
  filter(!is.na(time_read)) %>%
  mutate(did_mc = !is.na(time_check),
         passed_both_mc = man_check_cgo_correct & 
           man_check_emi_correct,
         started_assignment = !is.na(time_ready),
         completed_assignment = !is.na(time_assignment),
         is_in_sample = completed_assignment & passed_both_mc) %>%
  left_join(sent_wave) -> sample_screens

sample_screens %>%
  summarize(group = "Total",
            emails_sent = sum(sent_wave$emails_sent),
            responded = n(),
            response_rate = n()/sum(sent_wave$emails_sent),
            received_tment = n(),
            did_mc = sum(did_mc)/n(), 
            passed_both_mc = sum(passed_both_mc, na.rm = TRUE)/n(), 
            started_assignment = sum(started_assignment)/n(),
            completed_assignment = sum(completed_assignment)/n(),
            in_sample = sum(is_in_sample)/n(),
            n_in_sample = sum(is_in_sample)) -> sample_total

sample_screens %>%
  group_by(group) %>%
  summarize(emails_sent = as.integer(min(emails_sent)),
            responded = n(),
            response_rate = n()/min(emails_sent),
            did_mc = sum(did_mc)/n(), 
            passed_both_mc = sum(passed_both_mc, na.rm = TRUE)/n(), 
            started_assignment = sum(started_assignment)/n(),
            completed_assignment = sum(completed_assignment)/n(),
            in_sample = sum(is_in_sample)/n(),
            n_in_sample = sum(is_in_sample)) %>%
  ungroup() %>%
  rbind(sample_total %>% select(-received_tment)) %>%
  mutate_if(is.integer, comma) %>%
  mutate_if(is.double, percent, accuracy = 0.1) -> resp_table


resp_table %>%
  kable(col.names = c("Group", 
                      "# emails sent", 
                      "# responded", 
                      "Response rate",
                      "Did manipulation checks",
                      "Passed both manipulation checks",
                      "Started assignment",
                      "Completed assignment",
                      "Included in test sample",
                      "# in test sample"),
        align="lrrrrrrrrr") %>%
  kable_styling() %>%
  row_spec(7, bold = T) 

sample_screens %>%
  group_by(treatment) %>%
  summarize(received_tment = n(),
            did_mc = sum(did_mc)/n(), 
            passed_both_mc = sum(passed_both_mc, na.rm = TRUE)/n(), 
            started_assignment = sum(started_assignment)/n(),
            completed_assignment = sum(completed_assignment)/n(),
            in_sample = sum(is_in_sample)/n(),
            n_in_sample = sum(is_in_sample)) %>%
  ungroup() %>%
  rbind(sample_total %>% 
          select(-emails_sent, -responded, -response_rate) %>%
          rename(treatment = group)) %>%
  mutate(treatment = case_when(
    treatment == "1" ~ "Strong CG\nNo EMI", 
    treatment == "2" ~ "Strong CG\nEMI",
    treatment == "3" ~ "Weak CG\nNo EMI", 
    treatment == "4" ~ "Weak CG\nEMI",
    TRUE ~ "Total"
  )) %>%
  mutate_if(is.integer, comma) %>%
  mutate_if(is.double, percent, accuracy = 0.1) -> tment_table

tment_table %>%
  kable(col.names = c("Treatment", 
                      "# treated",
                      "Did manipulation checks",
                      "Passed both manipulation checks",
                      "Started assignment",
                      "Completed assignment",
                      "Included in test sample",
                      "# in test sample"),
        align="lrrrrrrr") %>%
  kable_styling() %>%
  row_spec(5, bold = T) 
```


```{r sample_construction}
li <- read_csv("online_experiment/data/online_exp_line_items.csv")

resp %>% 
  filter(!is.na(time_assignment)) %>%
  select(id, treatment, man_check_cgo_correct, 
         man_check_emi_correct, li$var[!li$fixed]) -> complete_wide

complete_wide %>%
   filter(
     man_check_cgo_correct,
     man_check_emi_correct
   ) -> passed_mc_wide

complete_wide %>%
  gather(key = "line_item", value = "included", 
         -id, -treatment, -man_check_cgo_correct, -man_check_emi_correct) %>%
  mutate(id = factor(id),
         line_item = factor(line_item, levels = li$var[!li$fixed]),
         treated_cg = treatment > 2,
         treated_em = treatment %in% c(2,4)) -> complete_long

complete_long %>%
   filter(
     man_check_cgo_correct,
     man_check_emi_correct
   ) -> passed_mc_long
```

## Response times by treatment

``` {r response_times}
df <- resp %>%
  filter(!is.na(time_assignment)) %>%
  mutate(passed_mc = man_check_cgo_correct == "TRUE" & man_check_emi_correct == "TRUE",
         treatment = factor(treatment, labels = c("Strong CG\nNo EMI", "Strong CG\nEMI",
                                                "Weak CG\nNo EMI", "Weak CG\nEMI"))) %>%
  select(treatment, passed_mc, time_read, time_check, time_ready, time_assignment)

ggplot(data = df[df$time_read < 240,], 
       aes(x = treatment, y = time_read, color = passed_mc)) +
  geom_boxplot() + theme_minimal()

ggplot(data = df[df$time_assignment < 600,], 
       aes(x = treatment, y = time_assignment, color = passed_mc)) +
  geom_boxplot() + theme_minimal()

```


## Probability of line item inclusion overall

``` {r figure_line_item_inclusion}
df <- complete_long
df$line_item <- factor(df$line_item, 
                       labels = str_wrap(li$line_item[!li$fixed], 10))

ggplot(df, aes(x = line_item, y = as.numeric(included))) +
  stat_summary(fun.y = mean, geom = "bar", color = "lightblue", fill = "lightblue") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") +
  scale_y_continuous(name = "Percentage of respondents that include",
                     labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(name ="Line item") + 
  theme_minimal() 

```

## Test for difference accross relevant line items

```{r test_li}
passed_mc_wide %>%
  select(fvg_market, fvg_model, gains_inv_property) -> df
t.test(df$fvg_market, df$fvg_model)
t.test(df$fvg_market, df$gains_inv_property)

passed_mc_long %>%
  filter(line_item == "fvg_market" | line_item == "fvg_model") %>%
  select(line_item, included) %>%
  droplevels() -> df
tb <- table(df)
tb
chisq.test(tb)

passed_mc_long %>%
  filter(line_item == "fvg_market" | line_item == "gains_inv_property") %>%
  select(line_item, included) %>%
  droplevels() -> df
tb <- table(df)
tb
chisq.test(tb)

```


## Probability of gain line item inclusion by treatment

```{r figure_gain_line_items_by_tment}
passed_mc_long %>%
  filter(line_item != "sga",
         line_item != "da",
         line_item != "int_exp",
         line_item != "tax_exp") %>%
  mutate(line_item = factor(line_item, levels = li$var[!li$fixed],
                            labels = paste0(str_wrap(li$line_item[!li$fixed], 10), "\n")))-> df

ggplot(df, aes(x = as.factor(treatment), 
               y = as.numeric(included), 
               color = line_item)) +
  stat_summary(fun.y = mean, geom = "point", 
               size = 2, position = position_dodge(0.2)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = 0.2, position = position_dodge(0.2)) +
  theme_minimal() + 
  scale_x_discrete(name = "Treatment", 
                   labels = c("Strong CG\nNo EMI", "Strong CG\nEMI",
                              "Weak CG\nNo EMI", "Weak CG\nEMI")) +
  scale_y_continuous(name = "Probability of inclusion",
                     labels = scales::percent_format(accuracy = 0.5)) +
  scale_color_discrete(name = "Line item")
```


## Difference between discretionary and non-discretionary line item inclusion probability by treatment

``` {r figure_dprob_disc_non_disc}
passed_mc_wide %>%
  mutate(dinclude = 0.5*fvg_model + 0.5*gains_inv_property - fvg_market,
         treated_cg = treatment > 2,
         treated_em = treatment %in% c(2,4)) %>%
  select(id, treatment, treated_em, treated_cg, dinclude) -> man_desc_sample

ggplot(man_desc_sample, aes(x = as.factor(treatment), y = dinclude)) +
  stat_summary(fun.y = mean, geom = "point", 
               size = 2) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  theme_minimal() + 
  scale_x_discrete(name = "Treatment", 
                   labels = c("Strong CG\nNo EMI", "Strong CG\nEMI",
                              "Weak CG\nNo EMI", "Weak CG\nEMI")) +
  scale_y_continuous(name = paste("Percentage point difference in inclusion",
                                  "probability for gain line items without", 
                                  "and with managerial discretion", sep = "\n"),
                     labels = unit_format(scale = 100, unit = "pp", accuracy = 0.5))
```


## Treatment effects for discretionary gain line items relative to non-discretionary gain litem

``` {r figure_tment_effect_disc_rel_to_non_disc}
df <- rbind(cbind(manipulation = "cg", man_desc_sample %>%
              rename(treated = treated_cg) %>%
                select(id, treated, dinclude)),
      cbind(manipulation = "em", man_desc_sample %>%
              rename(treated = treated_em) %>%
              select(id, treated, dinclude)))

ggplot(df, aes(x = treated, y = dinclude, color = manipulation)) +
  stat_summary(fun.y = mean, geom = "point", 
               size = 2, position = position_dodge(0.5)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.5), width = 0.2) +
  theme_minimal() + 
  scale_x_discrete(name = "Treated?", labels = c("No", "Yes")) +
  scale_y_continuous(name = paste("Percentage point difference in inclusion",
                                  "probability for gain line items without", 
                                  "and with managerial discretion", sep = "\n"),
                     labels = unit_format(scale = 100, unit = "pp", accuracy = 0.5)) + 
  scale_color_discrete(name = "Treatment",
                       labels = c("Weak CG", "EM Incentives")) +
  theme(legend.position = c(0.8, 0.2))
```


## Subject-level analysis

``` {r sub_lev_analysis}
lin_mod <- lm(dinclude ~ treated_cg + treated_em, data = man_desc_sample)
summary(lin_mod)
lin_mod <- lm(dinclude ~ treated_cg*treated_em, data = man_desc_sample)
summary(lin_mod)
Anova(lin_mod, type = "II")
Anova(lin_mod, type = "III")
linearHypothesis(lin_mod, "treated_cgTRUE + 0.5*treated_cgTRUE:treated_emTRUE = 0")
linearHypothesis(lin_mod, "treated_emTRUE + 0.5*treated_cgTRUE:treated_emTRUE = 0")

ord_mod <- MASS::polr(as.factor(dinclude) ~ treated_cg*treated_em, data = man_desc_sample)
ctable <- coef(summary(ord_mod))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
kable(ctable[1:3,], format.args = list(scientific = F, digits = 3)) %>%
  kable_styling()
Anova(ord_mod, type = "II")

kruskal.test(man_desc_sample$dinclude, man_desc_sample$treated_cg)
kruskal.test(man_desc_sample$dinclude, man_desc_sample$treated_em)
kruskal.test(man_desc_sample$dinclude, man_desc_sample$treated_em & man_desc_sample$treated_cg)
```


## Line-item level analysis

```{r li_lev_analysis, results="asis"}
passed_mc_wide %>%
  select(id, treatment, li$var[!li$fixed]) %>%
  gather(key = "line_item", value = "included", -id, -treatment) %>%
  mutate(id = as.factor(id),
         line_item = factor(line_item, levels = li$var[!li$fixed]),
         treated_cg = treatment > 2,
         treated_em = treatment %in% c(2,4),
         man_desc = line_item == "fvg_model" | line_item == "gains_inv_property",
         md_tcg = man_desc & treated_cg,
         md_tem = man_desc & treated_em) -> long_df

reg <- prepare_regression_table(long_df, c(rep("included", 6)), 
                         list(c("0", "line_item", "treated_cg"),
                              c("0", "line_item", "treated_cg", "md_tcg"),
                              c("0", "line_item", "treated_em"),
                              c("0", "line_item", "treated_em", "md_tem"),
                              c("0", "line_item", "treated_cg*treated_em"),
                              c("0", "line_item", "treated_cg*treated_em", "md_tcg*md_tem")),
                         models = c(rep("ols", 6)),
                         cluster = c(rep("id", 6)),
                         format = "html")
cat(paste(reg$table, collapse = "\n"))  

long_df %>%
  filter(line_item != "sga",
         line_item != "da",
         line_item != "int_exp",
         line_item != "tax_exp") -> long_df_pos_litems

reg <- prepare_regression_table(long_df_pos_litems, c(rep("included", 4)), 
                         list(c("0", "line_item", "treated_cg", "md_tcg"),
                              c("0", "line_item", "treated_em", "md_tem"),
                              c("0", "line_item", "treated_cg*treated_em"),
                              c("0", "line_item", "treated_cg*treated_em", "md_tcg*md_tem")),
                         models = c(rep("ols", 4)),
                         cluster = c(rep("id", 4)),
                         format = "html")
cat(paste(reg$table, collapse = "\n"))  

reg <- prepare_regression_table(long_df_pos_litems, c(rep("included", 3)), 
                         list(c("line_item", "md_tcg"),
                              c("line_item", "md_tem"),
                              c("line_item", "md_tcg*md_tem")),
                         models = c(rep("ols", 3)),
                         feffects = c(rep("id", 3)),
                         cluster = rep(list(c("id", "line_item")), 3),
                         format = "html")
cat(paste(reg$table, collapse = "\n")) 

reg <- prepare_regression_table(long_df_pos_litems, c(rep("included", 3)), 
                         list(c("md_tcg"),
                              c("md_tem"),
                              c("md_tcg*md_tem")),
                         models = c(rep("ols", 3)),
                         feffects = rep(list(c("id", "line_item")), 3),
                         cluster = rep(list(c("id", "line_item")), 3),
                         format = "html")
cat(paste(reg$table, collapse = "\n")) 

reg <- prepare_regression_table(long_df_pos_litems, c(rep("included", 3)), 
                         list(c("md_tcg"),
                              c("md_tem"),
                              c("md_tcg*md_tem")),
                         models = c(rep("ols", 3)),
                         feffects = rep(list(c("id", "line_item")), 3),
                         cluster = rep(list("id"), 3),
                         format = "html")
cat(paste(reg$table, collapse = "\n")) 

reg <- prepare_regression_table(long_df_pos_litems, c(rep("included", 3)), 
                         list(c("md_tcg"),
                              c("md_tem"),
                              c("md_tcg*md_tem")),
                         models = c(rep("ols", 3)),
                         feffects = rep(list(c("id", "line_item")), 3),
                         format = "html")
cat(paste(reg$table, collapse = "\n")) 
```
